Figures to insert in text

### 2018-03-15 Chapters/Chapter02.tex
details
SDM Conclusion i vs l

I have run the classification algorithm under the MNIST database of handwritten digits \citep{deng2012mnist}. First, SDM has been trained with the 60,000 training images, and then it classified the 10,000 testing images. In these initial tests, the memory has given the correct classification for 77.22\% of the images, which is inferior to the specialized algorithms. For instance, in 1998, \citet{lecun1998gradient} have developed algorithms which achieve from 88\% through a linear classifier, to 99.7\% through a convolutional net. For a review of algorithms' performance in the MNIST database, see \cite{mnist}.

@@

Of course, for the skeptical reader who may consider software a less worthy pursuit, there is also new work here.  The mathematics of the model has been shown to be correct numerically (with a single, small, anomaly); we have shown how to execute unsupervised learning with nothing besides operations original to the SDM; we have studied the generalized Murilo read; we have seen noise filtering; the death of neurons; how information-theory may be of use; and finally, we have reproduced numerous of the original propositions put forth by Kanerva.  The emphasis might have been on \emph{breadth of topics}, in detriment of depth here or there.  But this is due to our research group's enthusiam for the topic; we do indeed believe that SDM is --- if not correct --- extremely close to a full scientific understanding of human long-term memory.  If so, it is such a monumental achievement that we want readers to be able to see all of what we see and imagine the vastness of possibilities.  The work on, say, reinforcement learning, is most definitely not the definitive work we will see on the subject, but a challenge left for readers to contemplate. Ralph Waldo Emerson once said \emph{do not go where the path may lead. Go, instead, where there is no path, and leave a trail.}  Pentti Kanerva has left the trail.  It is my job to illuminate it and to pave it and to clear it; to try to deliver an easier pathway for the next generation.  Some essays completely shut the door close at the end; this one intends to leave it wide open. As the reader might have noticed, this final section does not read as an analysis of the work done; it reads, instead, as a \emph{desiderata}, a prologue, a yearning for others to join me in imagining the shape of things to come.

>>>>

I have run the classification algorithm under the MNIST database of handwritten digits \citep{deng2012mnist}. First, SDM has been trained with the 60,000 training images, and then it classified the 10,000 testing images. In these initial tests, the memory has given the correct classification for 79.22\% of the images, which is inferior to the specialized algorithms. For instance, in 1998, \citet{lecun1998gradient} have developed algorithms which achieve from 88\% through a linear classifier, to 99.7\% through a convolutional net. For a review of algorithms' performance in the MNIST database, see \cite{mnist}.

@@

Of course, for the skeptical reader who may consider software a less worthy pursuit, there is also new work here.  The mathematics of the model has been shown to be correct numerically (with a single, small, anomaly); we have shown how to execute unsupervised learning with nothing besides operations original to the SDM; we have studied the generalized Murilo read; we have seen noise filtering; the death of neurons; how information-theory may be of use; and finally, we have reproduced numerous of the original propositions put forth by Kanerva.  The emphasis might have been on \emph{breadth of topics}, in detriment of depth here or there.  But this is due to our research group's enthusiam for the topic; we do indeed believe that SDM is --- if not correct --- extremely close to a full scientific understanding of human long-term memory.  If so, it is such a monumental achievement that we want readers to be able to see all of what we see and imagine the vastness of possibilities.  The work on, say, reinforcement learning, is most definitely not the definitive work we will see on the subject, but a challenge left for readers to contemplate. Ralph Waldo Emerson once said \emph{do not go where the path may lead. Go, instead, where there is no path, and leave a trail.}  Professor Pentti Kanerva has left the trail.  It is my job to illuminate it and to pave it and to clear it; to try to deliver an easier pathway for the next generation.  Some essays completely shut the door close at the end; this one intends to leave it wide open. As the reader might have noticed, this final section does not read as an analysis of the work done; it reads, instead, as a \emph{desiderata}, a prologue, a yearning for others to join me in imagining the shape of things to come.
